Clustering time series based on probability distributions across temporal granularities

### 2021-11-14 main.Rmd
no additional gain in increasing nclust  from 3 for wpd-based

```{r opt-clusters}
knitr::include_graphics("figs/opt_clusters.png")
```

@@

```{r parcoord, fig.cap="Each of the $24$ customers is represented by a parallel coordinate plot (a) with three wpd-based groupings. Plot (b) which shows median wpd values for each group. The plot shows that moy is the most important variable in identifying clusters, whereas wnwd is the least significant and has the least fluctuation. Two customers (id: 16 and 18) with high wpd across wnwd stand out in this display. Group 3 has a higher wpd for hod than moy or wkndwday. Group 2 has most discernible pattern across moy. Group 1 is a mixed group with strong patterns on atleast one of the three variables. All of these could be observed from the plot or the table (b).", message=FALSE, warning=FALSE}
include_graphics("figs/parcoord-application.png")
```

>>>>

<!-- The widest within-cluster gap (widest_gap) is high till $k=5$ and then have a gradual decrease. Number of -->

```{r opt-clusters, fig.cap=" Different cluster statistics plotted as a function of number of clusters for JS-based (a) and wpd-based (b) approaches. avg within is not too useful for revealing any sharp change in average distance between clusters with increasing number of clusters. For (a), sindex sees a sharp fall at $k = 4$ and then do not decrease until $k=16$ and the widest gap is high till $k=5$. For (b), sindex sees a fall at $k=3$ and then at $k=7$ and widest gap has a sharp fall at $k=6$."}

#knitr::include_graphics("figs/opt_clusters.png")
```

@@

```{r parcoord-application, fig.cap="Each of the $24$ customers is represented by a parallel coordinate plot (a) with three wpd-based groupings. Plot (b) which shows median wpd values for each group. The plot shows that moy is the most important variable in identifying clusters, whereas wnwd is the least significant and has the least fluctuation. Two customers (id: 16 and 18) with high wpd across wnwd stand out in this display. Group 3 has a higher wpd for hod than moy or wkndwday. Group 2 has most discernible pattern across moy. Group 1 is a mixed group with strong patterns on atleast one of the three variables. All of these could be observed from the plot or the table (b).", message=FALSE, warning=FALSE, fig.height=6}
#include_graphics("figs/parcoord-application.png")
```
